---
title: "Sentiment update"
author: "Whitney Bullock"
date: "2025-07-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 
## Loading packages 

```{r}

warning(suppressMessages(library(tidyverse))) 
library(quanteda)
library(janitor)
library(here)
library(skimr)
library(sentimentr)
library(caret)
library(broom)
library(tidyverse)
library(readtext)
library(dplyr)
library(tidyr)



```


## Reading in Data 


```{r}

raw_reviews <- read_csv(here("top 240 restaurants recommanded in los angeles 2.csv")) %>% 
  clean_names()

# Create factor vars 
raw_reviews <- raw_reviews %>% 
  mutate(across(c(style, price), factor))

```

# Filtering for Korean restaurants 
```{r}
Korean_reviews <- raw_reviews %>% 
  filter(restaurant_name != "The Barn Cafe & Restaurant") %>% 
  filter(str_detect(style, "Korean"))
```


```{r}
Korean_restaurants <- raw_reviews %>%
  filter(str_detect(as.character(style), regex("korean", ignore_case = TRUE))) %>%
  group_by(restaurant_name) %>%
  summarise(
    best_rank = min(rank),              # Best (lowest) rank among entries
    avg_star_rating = mean(star_rating), # Average star rating
    total_reviews = sum(number_of_reviews), # Sum of reviews
    style = first(style)                # Pick first style as representative
  ) %>%
  arrange(best_rank)

print(Korean_restaurants)

head(Korean_restaurants,n=10)
tail(Korean_restaurants,n=10)
```


### Spliting Korean Restaurants into top and low ranking 

```{r}
# High rated restaurants
top_korean_spots <- raw_reviews %>% 
  filter(str_detect(style, "Korean"),
         rank < 26)

# Low rated Korean Restaurants
bad_korean_spots <- raw_reviews %>% 
  filter(restaurant_name != "The Barn Cafe & Restaurant") %>% 
  filter(str_detect(style, "Korean"),
         rank > 150) 
```

## Creating a corpus 

```{r}
corp_rest <- quanteda::corpus(Korean_reviews$comment)
summary(corp_rest, n=10)
```

```{r}
corp_top <- quanteda::corpus(top_korean_spots$comment)
summary(corp_top, n=10)

corp_bad <- quanteda::corpus(bad_korean_spots$comment)
summary(corp_bad, n=10)

```

### Tokenizing 

```{r}
Korean_reviews <- raw_reviews %>%
  filter(str_detect(style, regex("korean", ignore_case = TRUE))) %>%
  filter(!is.na(comment))  # Ensure no missing comments

# Create a quanteda corpus explicitly
corp_rest <- quanteda::corpus(Korean_reviews$comment)

# Define custom stopwords
custom_stopwords <- c(stopwords("en"), "restaurant", "food", "place")

# Tokenize
reviews_tokens <- quanteda::tokens(corp_rest,
                                   remove_punct = TRUE,
                                   remove_numbers = TRUE,
                                   remove_symbols = TRUE) %>%
                  tokens_remove(pattern = custom_stopwords)

```

## Prepping for sentiment analysis 

```{r}
test.lexicon <- dictionary(list(positive.terms = c("happy", "joy", "light"), 
                                negative.terms = c("sad", "angry", "darkness")))
```

```{r}
positive_words_bing <- scan("positive-words.txt", what = "char", sep = "\n", skip = 35, quiet = T)
negative_words_bing <- scan("negative-words.txt", what = "char", sep = "\n", skip = 35, quiet = T)
sentiment_bing <- dictionary(list(positive = positive_words_bing, negative = negative_words_bing))

```


```{r}
sentiment.dictionary <- dictionary(list(positive = positive_words_bing, negative = negative_words_bing))
str(sentiment.dictionary)

```

## DFM 

```{r}
dfm_reviews <- dfm(reviews_tokens)

dfm_sentiment <- dfm_lookup(dfm_reviews, dictionary = sentiment.dictionary)

head(dfm_sentiment)
```




```{r}

dfm_sentiment_df<-convert(dfm_sentiment, to ='data.frame')
dfm_sentiment_df$net<-(dfm_sentiment_df$positive)-(dfm_sentiment_df$negative)
summary(dfm_sentiment_df)# document level summary

install.packages("remotes")
remotes::install_github("kbenoit/quanteda.dictionaries")

library("quanteda.dictionaries")
output_mfd <- quanteda.dictionaries::liwcalike(corp_rest, 
                        dictionary = data_dictionary_MFD)
head(output_mfd)



```



```{r}
dfm_sentiment_prop <- dfm_weight(dfm_sentiment, scheme = "prop")
head(dfm_sentiment_prop)

```

### Sentiment Scores 

```{r}
sentiment <- convert(dfm_sentiment_prop, "data.frame") %>%
    gather(positive, negative, key = "Polarity", value = "Share") %>% 
    mutate(document = as_factor(doc_id)) %>% 
    rename(Review = document)

ggplot(sentiment, aes(Review, Share, fill = Polarity, group = Polarity)) + 
    geom_bar(stat='identity', position = position_dodge(), size = 1) + 
    scale_fill_brewer(palette = "Set1") + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
    ggtitle("Sentiment scores in Korean Restaurant Reviews (relative)")

```

### Average Sentiment by Restaurant name 

```{r}
out <- with(
    Korean_reviews, 
    sentiment_by(
        get_sentences(comment), 
        list(restaurant_name,price)
    ))
head(out, n=10)

```

### Highlight positive and negative phrases within 6 reviews from all Korean Restaurants, top ranking Korean Restaurants, and poor ranking Korean Restaurants 

```{r}
library(magrittr)
library(dplyr)
set.seed(123)

Korean_reviews %>%
    filter(restaurant_name %in% sample(unique(restaurant_name), 6)) %>% 
    # %in% operator in R, is used to identify if an element belongs to a vector.
    mutate(review = get_sentences(comment)) %$%
    # The “exposition” pipe operator from magrittr package, %$% exposes the names  
    # within the left-hand side object to the right-hand side expression. For  
    # instance,
    # iris %>%
    # subset(Sepal.Length > mean(Sepal.Length)) %$%
    # cor(Sepal.Length, Sepal.Width)
    sentiment_by(comment, restaurant_name) %>%
    highlight()


library(tidyverse)
library(cleanNLP)

```

### Visualized Emotions 

```{r}
# Load required libraries
library(syuzhet)
library(tidyverse)

# Read CSV
raw_review2 <- read_csv("top 240 restaurants recommanded in los angeles 2.csv")

korean_reviews22 <- raw_review2 %>%
  filter(str_detect(tolower(Style), "korean"))


# Take a random sample of 500 rows
set.seed(123)
raw_reviews22 <- slice_sample(korean_reviews22, n = 100)

# Run NRC sentiment analysis on the 'comment' column
nrc_data <- get_nrc_sentiment(raw_reviews22$Comment)

# Combine sentiment scores with the original data
df_combined <- bind_cols(raw_reviews22, nrc_data)

# ------------------------
# Visualization
# ------------------------

# Transpose the sentiment data for aggregation
td <- data.frame(t(nrc_data))

# Sum sentiment counts across all comments
td_new <- data.frame(rowSums(td[1:ncol(td)]))

# Rename and reshape for plotting
names(td_new)[1] <- "count"
td_new <- cbind(sentiment = rownames(td_new), td_new)
rownames(td_new) <- NULL

# Plot: count of words associated with each sentiment
ggplot(td_new, aes(x = sentiment, y = count, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ggtitle("Restaurant Sentiments (NRC)") +
  ylab("Review Count") +
  xlab("Sentiment") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


## Consolidated view of all Seong Buk Dong reviews 

```{r}
seongbuk_reviews <- Korean_reviews %>%
  filter(restaurant_name == "Seong Buk Dong")

print(seongbuk_reviews$comment)

```

## Sentiment score for each review of Seong Buk Dong 

```{r}
library(dplyr)
library(sentimentr)

reviews_25 <- Korean_reviews %>%
  filter(restaurant_name == "Seong Buk Dong") %>%
  slice_head(n = 25)

sentiment_each_review <- sentiment(reviews_25$comment)

library(tidyr)

sentiment_summary <- sentiment_each_review %>%
  group_by(element_id) %>%
  summarize(
    sentiment = mean(sentiment),
    review = first(get_sentences(reviews_25$comment[element_id]))
  )

print(sentiment_summary)

```


### NRC score for Seong Buk Dong 

```{r}
library(syuzhet)
library(tidyverse)


seong_reviews <- Korean_reviews %>% 
  filter(restaurant_name == "Seong Buk Dong")

# Run NRC sentiment analysis on the 'comment' column
nrc_data_seong <- get_nrc_sentiment(seong_reviews$comment)

# Combine sentiment scores with original review data
df_combined_seong <- bind_cols(seong_reviews, nrc_data_seong)

# ------------------------
# Visualization
# ------------------------

# Transpose for aggregation
td_seong <- data.frame(t(nrc_data_seong))

# Sum sentiment counts across all comments
td_new_seong <- data.frame(rowSums(td_seong[1:ncol(td_seong)]))

# Rename and reshape for plotting
names(td_new_seong)[1] <- "count"
td_new_seong <- cbind(sentiment = rownames(td_new_seong), td_new_seong)
rownames(td_new_seong) <- NULL

# Plot sentiment counts
library(ggplot2)

ggplot(td_new_seong, aes(x = sentiment, y = count, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ggtitle("NRC Sentiment for Seong Buk Dong") +
  ylab("Word Count") +
  xlab("Sentiment") +
  theme_minimal() +
  theme(
    plot.background = element_rect(fill = "black", color = NA),
    panel.background = element_rect(fill = "black", color = NA),
    panel.grid.major = element_line(color = "gray30"),
    panel.grid.minor = element_line(color = "gray20"),
    axis.text = element_text(color = "white"),
    axis.title = element_text(color = "white"),
    plot.title = element_text(color = "white"),
    legend.position = "none"
  )
```

### LDA specific to Seong Buk Dong 

```{r}

# Load necessary libraries
library(tm)
library(SnowballC)
library(topicmodels)
library(tidytext)
library(dplyr)
library(ggplot2)
library(tidyr)  # For 'reorder_within' function
library(scales) # For plotting
library(textstem)

# Filter reviews for one restaurant
seong_reviews1 <- Korean_reviews %>%
  filter(restaurant_name == "Seong Buk Dong") %>%
  pull(comment)

# Create a corpus
corp_seong <- VCorpus(VectorSource(seong_reviews1))

# Define enhanced custom stopwords
custom_stopwords <- c(stopwords("english"), 
                      "also", "use", "used", "food", 
                      "restaurant", "korean", "korea", 
                      "kalbi", "like", "just", "really", 
                      "order", "came", "get", "got", 
                      "this", "that", "you", "your", "they")

# Clean and stem the corpus
corp_seong_clean <- corp_seong %>%
  tm_map(content_transformer(tolower)) %>%
  tm_map(removePunctuation) %>%
  tm_map(removeNumbers) %>%
  tm_map(removeWords, custom_stopwords) %>%
  tm_map(stripWhitespace) %>%
  tm_map(content_transformer(lemmatize_strings))

# Create Document-Term Matrix from cleaned corpus
dtmbad <- DocumentTermMatrix(corp_seong_clean)

# Remove sparse terms
dtmfilteredbad <- removeSparseTerms(dtmbad, 0.98)

# Train LDA model
lda_model_seong <- LDA(dtmfilteredbad, k = 3, control = list(seed = 123))

# Tidy topic-word matrix
term_topics_seong <- tidy(lda_model_seong, matrix = "beta")

# Get top terms per topic
top_terms_seong <- term_topics_seong %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Plot top terms per topic
top_terms_seong %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(x = term, y = beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~topic, scales = "free_y") +
  coord_flip() +
  scale_x_reordered() +
  labs(title = "Top Terms in each LDA Topic for Seong Buk Dong",
       x = "Terms", y = "Probability (Beta)")

```

```{r}

terms(lda_model_seong,10)

```

